ARGoS-Blockchain interface

### 2020-09-12 article.tex
code easier to copy

\item Additionally, restarting the Docker engine via \verb|systemctl|
  requires sudo privileges. To control Docker as a normal user, add an
  entry in the sudoers file.
\begin{verbatim}
$ sudo visudo -f /etc/sudoers.d/docker
volker ALL= NOPASSWD: /bin/systemctl restart docker.service
volker ALL= NOPASSWD: /bin/systemctl start docker.service
volker ALL= NOPASSWD: /bin/systemctl stop docker.service
\end{verbatim}
\end{enumerate}

>>>>

\item Additionally, restarting the Docker engine via \verb|systemctl|
  requires sudo privileges. To control Docker as a normal user, add an
  entry in the sudoers file (replace \verb|volker| with your user
  name).
\begin{verbatim}
$ sudo visudo -f /etc/sudoers.d/docker
\end{verbatim}
\begin{verbatim}
volker ALL= NOPASSWD: /bin/systemctl restart docker.service
volker ALL= NOPASSWD: /bin/systemctl start docker.service
volker ALL= NOPASSWD: /bin/systemctl stop docker.service
\end{verbatim}
\end{enumerate}
